Dataset Documentation

### 2016-01-29 dataset/Documentation/Readme.Rmd
doc figs

We use Compustat to get the annual BE/ME ratios of the firm as described in Appendix 1 of 
*Disappearing dividends: changing firm characteristics or lower propensity to pay?, Fama-French, JFE 2001*:

@@

@@

>>>>

We use Compustat to get the annual BE/ME ratios of the firm as described in Appendix 1 of 
[Disappearing dividends: changing firm characteristics or lower propensity to pay?, Fama-French, JFE 2001](http://www.ulb.ac.be/cours/solvay/farber/Ofin/Reading%206%20Disappearing%20dividend.pdf):

@@

![Preferred Stock and Book Equity equation variables ](fig3.png)

The Preferred Stock and Book Equity equation variables (except the Post Retirement Asset which we get from the Compustat Monthly Updates - Pension Annual Database) correspond to the following variables in the CRSP/Compustat Merged - Fundamentals Annual database, in the same order as they appear in the equation:

![Preferred Stock and Book Equity equation variables Selected](fig2.png)

@@

![(Draft) List of Dataset Variables](fig1.png)

At the end we have the following variables (for buybacks and issuers):

![(Draft) List of Dataset Variables](buybacks.png)

![(Draft) List of Dataset Variables](issuers.png)
